\speculake: Hiding Malware in Speculative Execution

### 2018-12-10 paper/architecture.tex
fix idiv numbers

We also tested whether instruction complexity or data dependencies impact the
number of instructions that can be completed. We find that data dependencies and
instruction complexity both have an impact on the number of instructions that
can be executed. Instruction complexity is determined by the number of $\mu$~ops
that the instruction uses, which appears to be what is tracked in the ROB. For
instance, on our architecture, the 64-bit \texttt{idiv} instruction takes 59~$\mu$~ops,
and we can execute up to 3 of them in the speculative world.
Meanwhile, we can execute up to 18 32-bit \texttt{idiv} instructions, which each
take 9~$\mu$~ops~\cite{intel-instruction-tables}. These suggest we can execute
on the order of 175~$\mu$~ops before the speculative world expires.

>>>>

We also tested whether instruction complexity or data dependencies impact the
number of instructions that can be completed. We find that data dependencies and
instruction complexity both have an impact on the number of instructions that
can be executed. Instruction complexity is determined by the number of $\mu$~ops
that the instruction uses, which appears to be what is tracked in the ROB. For
instance, on our Skylake architecture, the 64-bit \texttt{idiv} instruction
takes 57~$\mu$~ops, and we can execute up to 3 of them in the speculative world.
Meanwhile, we can execute up to 12 32-bit \texttt{idiv} instructions, which each
take 10~$\mu$~ops~\cite{intel-instruction-tables}. This suggest we can execute
on the order of 175~$\mu$~ops before the speculative world expires.
